Methods for Large Scale Learning to Rank

### 2014-04-04 report/Chapters/CrossBenchmarkComparison.tex
begin toevoegen references aan lijst methods

\section{Evaluation Results Found in Literature}

>>>>

\section{Evaluation Results Found in Literature}
\begin{table}[!h]
\begin{tabular}{l|l|l}
AdaRank-\acs{MAP} & \acs{GP}Rank & RankAgg\ac{nDCG} \\ 
AdaRank-\acs{nDCG} & GRank\acs{RLS} & RankBoost \\ 
ADMM & Group\acs{CE} \cite{Lin2011} & RankCSA \cite{He2010} \\ 
Approx\acs{AP} \cite{Qin2010b} & Group\acs{MLE} & RankDE \\ 
Approx\acs{nDCG} \cite{Qin2010b} & IntervalRank \cite{Moon2010} & RankELM (pairwise) \\ 
BagBoo & \acs{IP}Rank & RankELM (pointwise) \\ 
Best Single Feature & KeepRank & Ranking Committee Perceptron \cite{Elsas2008} \\ 
BL-MART \cite{Ganjisaffar2011c} & Kernel-\acs{PCA} & RankMGP \\ 
BoltzRank-Single \cite{Volkovs2009} & KL-\acs{CRF} & RankNet \\ 
BoltzRank-Pair \cite{Volkovs2009} & LAC-MR-OR \cite{Veloso2008} & Rank\ac{RLS} \\ 
BT \cite{Zhou2008} & LambdaMART & Rank\ac{SVM} \\ 
C-\acs{CRF} \cite{Qin2008b} & LambdaNeuralRank \cite{Papini2012} & Rank\ac{SVM}-Primal \\ 
\acs{CA} & LambdaRank & Rank\acs{SVM}-Struct \\ 
\ac{CC}Rank & LARF & RE-QR \\ 
CoList & Linear Regression & REG-SHF-SDCG \\ 
Consistent-RankCosine & List\acs{MLE} & Regression \\ 
DCMP \cite{Renjifo2012} & ListNet & Ridge Regression \\ 
DirectRank & ListReg & RSRank \\ 
Energy\ac{nDCG} \cite{Freno2011} & LRUF & SmoothGrad \\ 
FBPCRank \cite{Lai2011} & MBP & SmoothRank \\ 
FenchelRank \cite{Lai2013} & MHR & SoftRank \\ 
FocusedBoost \cite{Niu2012} & MultiStageBoost & SortNet \cite{Rigutini2008} \\ 
FocusedNet \cite{Niu2012} & NewLoss & SparseRank \\ 
Focused\ac{SVM} \cite{Niu2012} & OWPC & \acs{SVD}-RankBoost \cite{Lin2009} \\ 
FPRank & PERF-\ac{MAP} & \ac{SVM}$^{\ac{MAP}}$ \\ 
FRank & PermuRank \cite{Xu2008} & SwarmRank \\ 
FSMRank & Q.D.\acs{KNN} & TGRank \\ 
FSM$^{\acs{MAP}}$ & RandomForest & TM \cite{Zhou2008} \\ 
GAS-E & Rank-PMBGP \cite{Sato2013} & VFLR \\ 
\end{tabular}
\caption{Learning-to-Rank algorithms with measurements on benchmark datasets}
\label{ltr_methods_used}
\end{table}
